\documentclass[10pt]{article}
%
%Load the myriad packages
\usepackage{amssymb,amsmath}
\usepackage[margin=1.5cm]{geometry}
%\usepackage{textcomp}
%\usepackage{graphicx}
%\usepackage[dvips]{graphicx}
%\usepackage{tikz}
\usepackage{subfig}    % for multi-figure figures
%\usepackage[numbers, super]{natbib}
\usepackage{natbib}
%\usepackage{pdflscape}
%\usepackage{rotating}
%\usepackage{grffile} %spaces in file names
%\usepackage{parskip}
%\usepackage[T1]{fontenc} %for sc and bf
\usepackage{bigstrut}
\usepackage{hyperref}
\usepackage{float}
\usepackage{framed}
% Optional for code samples
\usepackage{listings}
\usepackage{multirow}
%
% misc.
\newcommand{\keff}{\ensuremath{{k_\mathrm{eff}}}}
\newcommand{\alphaT}{\ensuremath{{\alpha_{_T}}}}
\newcommand{\SN}{\ensuremath{{\text{S}_\text{N}}}}
%Note: tarticle has ``several'' changes from article
%in this vein.
% some simplifying commands
\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\etal}{{\it et al.}}
\newcommand{\E}{\mathcal{E}}
% derivative - d
\newcommand{\ud}{\,\mathrm{d}}
% bold unit vector n-hat
\newcommand{\nhat}{\hat{\bf n}}
\newcommand{\tensor}[1]{\mathcal{#1}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\varvec}[1]{\boldsymbol{#1}}
\newcommand{\om}{\boldsymbol{\Omega}}
\newcommand{\order}[1]{\ensuremath{\mathcal{O}\left(#1\right)}}

\newlength \figwidth
\setlength \figwidth {1\textwidth}

%
\begin{document}

\title{OpenMC: Pre-Competition Document \\for the 2018 Student Cluster Competition}

\maketitle

\begin{enumerate}
\item One application used in the 2018 SCC is OpenMC, an open-source Monte Carlo nuclear neutronics code originally created at MIT targeted at simulation of nuclear reactors
\item The OpenMC challenge will include an interview and a writeup. The problems will be nuclear-reactor-relevant. Most light-water reactors are made up of a lattice of pincells of fissile material.
\item Documentation on OpenMC is available at \url{http://openmc.readthedocs.io/en/stable/}
\item The source code for OpenMC may be downloaded at \url{https://github.com/mit-crpg/openmc}, or by using \linebreak\verb+git clone https://github.com/mit-crpg/openmc.git+
\item The OpenMC portion of the competition will require third-party software, including
    \begin{itemize}
    \item A compiler with Fortran support such as such gcc
     \item HDF5 compiled with Fortran support \\(\url{http://openmc.readthedocs.io/en/stable/usersguide/install.html#building-from-source})
     \item Python 3, for scripts included with OpenMC and/or the competition
     \item A PDF generator, for the report
    \end{itemize}
\item The test suite is useful for familiarizing oneself with input files for the code, running the code and ensuring correctness, and with exploring output files and format. The test suite is at \url{https://github.com/mit-crpg/openmc/tree/develop/tests}. A useful example is  \url{https://github.com/mit-crpg/openmc/tree/develop/examples/xml/lattice/simple}
\item Relevant theory for OpenMC may be found at \url{http://openmc.readthedocs.io/en/stable/methods/index.html}
\item OpenMC requires nuclear data in a specific format. Data is available at \url{http://www.nndc.bnl.gov/endf/b7.1/acefiles.html}. A script to download and prepare the data for OpenMC is referenced in {\footnotesize\url{http://openmc.readthedocs.io/en/stable/usersguide/cross_sections.html#using-endf-b-vii-1-cross-sections-from-nndc}}.
\item OpenMC is CPU-only. There is no GPU port of OpenMC. We do not recommend you develop such a GPU port, though we do not forbid it. If you do develop a GPU port, you are responsible for ensuring correctness, which we will test as part of the competition. Any changes you make to OpenMC (not recommended) must be posted publicly after the competition.
\end{enumerate}



\end{document}
